Missing data: Current practice in football research and recommendations for improvement

### 2020-09-04 paper/paper.Rmd
wording in the search method.
search method wording.

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@PRISMA]. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The PRISMA figure in Supplement 2 summarises the search process.

Our intention was to survey, at random, 10% of the total articles found, after 
title and abstract screening. We were primarily interested in
whether missing data was reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information relating to how missing
values were treated was also extracted (see Supplement 2). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval. 
Further details of the search can be found in Supplement 2.

>>>>

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@PRISMA]. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The PRISMA figure in Supplement 2 summarises the search process,
and further details of the search can also be found in Supplement 2.

Our intention was to survey, at random, 10% of the total articles found (after 
title and abstract screening). We were primarily interested in
whether missing data was reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information relating to how missing
values were treated was also extracted (see Supplement 2). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval.
